E1 Testing

### 2023-08-15 Analysis/e1_test.qmd
citation system setup in quarto

---
title: "E1 Testing"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
execute:
  echo: true
  message: true
  warning: true
---

@@

>>>>

---
title: "E1 Testing"
date: last-modified
categories: [Analysis, R, Bayesian]
#bibliography: ../Assets/Bib/htw.bib
code-fold: true
execute:
  echo: true
  message: true
  warning: true
editor: 
  markdown: 
    wrap: 72
---

Analyses were done using @burknerBrmsPackageBayesian2017 and
@makowskiBayestestRDescribingEffects2019a

[@deloshExtrapolationSineQua1997]

[@adkinsHeuristicsContributeSensorimotor2022]

@@

Here is a footnote reference,[^1] and another.[^2]

[^1]: Here is the footnote.

[^2]: Here's one with multiple blocks. Subsequent paragraphs are
    indented to show that they belong to the previous footnote.

    ```         
    { some.code }
    ```

    The whole paragraph can be indented, or just the first line. In this
    way, multi-paragraph footnotes work like multi-paragraph list items.

This paragraph won't be part of the note, because it isn't indented.

Here is an inline note.[^3]

[^3]: Inlines notes are easier to write, since you don't have to pick an
    identifier and move down to type the note.

### References

::: {#refs}
:::
